Supporting Ecological Decision Making Using Feature-Selection and Variable Importance

### 2020-03-03 docs/00-manuscripts/ieee/performance-best-per-learner.tex
update learner result tables

% latex table generated in R 3.6.1 by xtable 1.8-3 package
\begin{table}[ht!]
\centering
\caption{Best performance of each learner across any task and filter method.} 
\label{tab:best-learner-perf}
\scalebox{0.9}{
\begin{tabular}{rlllrr}
  \hline
 & Task & Model & Filter & RMSE & SE \\ 
  \hline
1 & HR & RF & Relief & 30.66 & 13.57 \\ 
  2 & HR & XGBoost & Borda & 30.75 & 13.75 \\ 
  3 & HR-NRI & SVM & Borda & 31.70 & 15.62 \\ 
  4 & NRI & Ridge-CV & No Filter & 33.31 & 8.17 \\ 
  5 & HR & Lasso-CV & No Filter & 47.22 & 20.52 \\ 
  6 & HR & Lasso-MBO & No Filter & 55.11 & 22.84 \\ 
  7 & HR & Ridge-MBO & No Filter & 55.11 & 22.84 \\ 
   \hline
\end{tabular}
}
\end{table}

>>>>

% latex table generated in R 3.6.3 by xtable 1.8-3 package
\begin{table}[ht!]
\centering
\caption{Best performance of each learner across any task and filter method.} 
\label{tab:best-learner-perf}
\scalebox{0.9}{
\begin{tabular}{rlllrr}
  \hline
 & Task & Model & Filter & RMSE & SE \\ 
  \hline
1 & HR-NRI & SVM & Car & 27.98 & 19.19 \\ 
  2 & HR-NRI & RF & Car & 31.08 & 17.09 \\ 
  3 & NRI\_VI & XGBOOST & Relief & 32.10 & 17.73 \\ 
  4 & NRI & Ridge-CV & No Filter & 32.97 & 7.24 \\ 
  5 & HR & Lasso-CV & No Filter & 45.96 & 18.35 \\ 
   \hline
\end{tabular}
}
\end{table}
